\section{Expected Contributions and Next Steps}
\label{sec:conclusion}

This proposal outlines a research design to test whether board observer networks serve as channels for private information flow between firms. The preliminary evidence is consistent with the hypothesis. When material events occur at private companies with board observers, connected public companies show abnormal returns of 4.6 percentage points (M\&A announcements) to 9.5 percentage points (bankruptcy filings) in the weeks before public disclosure. The effect is concentrated in same-industry connections and in events involving confidential board decisions. Routine corporate events produce no spillover.

Two regulatory changes offer a promising identification strategy. The NVCA's 2020 removal of fiduciary language from observer provisions coincides with an increase in same-industry spillover from zero to 3.0 percentage points. The DOJ/FTC's January 2025 extension of Clayton Act Section~8 to observers coincides with a reversal. These opposite-direction responses to independent regulatory changes, both with clean placebos, would support a causal interpretation if the pattern holds as the sample grows.

If the proposed research is successful, it would make three contributions to the literature. First, it would document a private-to-public information channel that prior work on interlocking directorates has not examined, one that operates through the Reg~FD exemption for private firms rather than through connections between public firms. Second, it would identify \textit{pre-event} information leakage rather than post-event reputation spillovers or decision mimicry. Third, it would provide quasi-experimental evidence from two regulatory shocks operating in opposite directions on the role of legal accountability in governing information flow through board networks.

The findings would also carry regulatory implications. The DOJ/FTC's decision to extend interlocking directorate rules to board observers would be empirically supported if same-industry observer connections indeed generate abnormal returns at connected firms before public disclosure. The NVCA's 2025 expansion of competitive harm carve-outs, which gives companies broader authority to exclude observers from sensitive discussions, would respond to a real information channel.

\subsection{Planned Extensions}

Several extensions would strengthen the analysis and are part of the proposed research plan.

\begin{enumerate}
\item \textbf{Sample expansion.} Incorporating events at public observed companies would approximately triple the sample and substantially improve statistical power, particularly for the bankruptcy and M\&A subsamples where connected same-industry observations are currently limited (11--28 observations).

\item \textbf{Calendar-time portfolios.} A calendar-time portfolio approach would serve as an alternative to event-time CARs, addressing concerns about overlapping event windows and cross-sectional dependence in returns.

\item \textbf{Mechanism and channel identification.} The preliminary results establish that information reaches prices through the observer network, but the specific transmission channel remains unidentified. I plan to investigate five candidate mechanisms.
\begin{enumerate}[label=(\alph*)]
\item \textit{Direct insider trading by the observer.} If the observer personally trades on information learned at the private firm's board, this should appear in their Form~4 filings at the connected public company. Preliminary Form~4 analysis is suggestive (buy share rises from 42\% to 63\% in pre-event windows) but underpowered. Expanding the sample and examining trade timing more precisely would sharpen this test.
\item \textit{VC-level portfolio rebalancing.} The observer reports back to their VC firm, which adjusts positions across portfolio companies in anticipation of the event. This channel would be detectable through 13F institutional holdings filings. If the VC fund increases its stake in same-industry portfolio companies before M\&A announcements at the observed firm.
\item \textit{Strategic decision-making at the connected public firm.} The observer, serving as a director at the public firm, may influence corporate decisions such as preemptive acquisitions, hiring, and capital allocation based on what they learned at the private firm's board. This channel would produce real effects (investment, employment) rather than purely financial ones, and could be tested using quarterly financial data around events.
\item \textit{Information diffusion through the VC ecosystem.} The observer shares information informally with colleagues, analysts, or limited partners, who then trade. This broader diffusion channel would predict that the effect is stronger for observers at larger, more connected VC firms and for firms with more institutional investor overlap. Network centrality measures and LP co-investment data could distinguish this channel.
\item \textit{Common investor rebalancing.} Institutional investors holding stakes in both the private and public firms, such as the VC's limited partners or crossover funds, may rebalance based on information flow. This would be testable through 13F data on overlapping institutional holders.
\end{enumerate}
Distinguishing among these channels is a central objective of the proposed research. The null result on abnormal volume (Appendix~A4) tentatively argues against concentrated trading by a single informed party, but more granular tests are needed.

\item \textbf{Post-shock data accumulation.} As additional post-January 2025 data accumulates, the Clayton Act effect can be estimated with greater precision. The October 2025 NVCA competitive harm provisions offer a third regulatory shock to be tested once sufficient post-event data exists.

\item \textbf{Network heterogeneity.} Analysis of whether the effect varies with observer characteristics, such as the number of simultaneous board seats, the observer's role at their VC firm, or the size of the VC fund, would illuminate which types of observers are most associated with information spillover.
\end{enumerate}

\subsection{Limitations}

Several limitations of the current analysis warrant acknowledgment. The observer network, while supplemented with BoardEx and Form~4 data, captures an estimated half of all observer-to-public-firm connections. The remaining connections would increase statistical power but cannot introduce spurious effects. The same-industry samples for M\&A and bankruptcy events are small, making coefficient estimates noisy despite their statistical significance. I do not identify the specific mechanism through which information reaches prices, though the regulatory responsiveness suggests the observer's legal position is a necessary condition. Finally, the post-January 2025 sample remains short, and the Clayton Act estimates should be treated as preliminary until additional data confirms the pattern.